Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
updated description for use case 8
finishing up use case about reproducing experience

@@

\niemnote{This one was not adopted into table; should we keep it, remote here, or somehow indicate why it was not adopted?}

@@

Requirements
\begin{itemize}
\item Name of software
\item Software version number
\item Documentation of the execution environment/context
\item Location/repository for virtual machine (or equivalent) comprising both software and execution environment/context
\item Persistent identifier associated with virtual machine instance (or equivalent) comprising both software and execution environment/context
\end{itemize}

Possible steps
\begin{enumerate}
\item Researcher obtains persistent ID from citation
\item Research uses a persistent ID resolution service to resolve ID to a location of  an executable VM instance in a repository
\item Researcher obtains VM in the repository, executes it, and interacts with software
\end{enumerate}

>>>>

This case asks what information regarding software is needed for a publisher who wants to publish a paper describing that software.

@@

@@

Requirements:
\begin{itemize}
\item Name of software
\item Software version number
\item Documentation of the execution environment/context
\item Location/repository for virtual machine (or equivalent) comprising both software and execution environment/context
\item Persistent identifier associated with virtual machine instance (or equivalent) comprising both software and execution environment/context
\end{itemize}

Possible steps:
\begin{enumerate}
\item Researcher obtains persistent ID from citation
\item Research uses a persistent ID resolution service to resolve ID to a location of  an executable VM instance in a repository
\item Researcher obtains VM in the repository, executes it, and interacts with software
\end{enumerate}

Due to overlaps with use case 6, reproducing analysis, we decided not to include
this use case in the table.
